A novel method for detecting coalescing binaries in near realtime with Advanced LIGO and beyond \editorial{Submit to PRD or CQG?}

### 2011-02-18 results.tex
added note about iligo versus aligo
git-svn-id: https://svn.ligo.caltech.edu/svn/6th-Floor-Papers/lloid_paper@642 ccdd05d5-56c1-461a-bf98-85f6876523b4
Added description of injection population
git-svn-id: https://svn.ligo.caltech.edu/svn/6th-Floor-Papers/lloid_paper@643 ccdd05d5-56c1-461a-bf98-85f6876523b4

We tested the new detection method with mock Advanced \textsc{ligo} data having a power spectrum prescribed by the ``zero detuning, high power'' noise model in \cite{Shoemaker:2009p9770}.  Colored Gaussian noise is generated by passing 5 independent realizations of white Gaussian noise sampled at 16384 Hz through a bank of 5 third-order \textsc{iir} filters, then summing the filters' outputs.  This carefully designed filter bank reproduces the noise model very faithfully, but since it is composed of \textsc{iir} filters it can produce mock data in realtime very cheaply.  See \ref{appendix:mock-data} for implementation details.

>>>>

We generated receiver operating characteristic (\textsc{roc}) curves for a selection of choices for the composite detection statistic threshold and the \textsc{svd} tolerance.  For each \textsc{roc} curve, or `run', we analyzed mock data with injections to assess detection efficiencies and mock data without injections to evaluate false alarm rates.

\subsection{Detector noise characteristics}

We tested the new detection method with mock Advanced \textsc{ligo} data having a power spectrum prescribed by the ``zero detuning, high power'' noise model in \cite{Shoemaker:2009p9770}.  Colored Gaussian noise is generated by passing 5 independent realizations of white Gaussian noise sampled at 16384 Hz through a bank of 5 third-order \textsc{iir} filters, then summing the filters' outputs.  This carefully designed filter bank reproduces the noise model very faithfully, but since it is composed of \textsc{iir} filters it can produce mock data in realtime very cheaply.  See \ref{appendix:mock-data} for implementation details. \editorial{In this section, we refer to aLIGO run parameters, but the results are actually using initial LIGO noise and initial LIGO parameters.  This will be fixed.}

\subsection{Injection population}

For each run, we performed about $10^4$ injections into our mock dataset.  Injections were 2PN post-Newtonian inspiral waveforms with component masses independently and identically distributed in $[1, 3]$ $M_\odot$.  Injections were tapered \editorial{Check --taper-injection option with Drew.} at a frequency of 10~Hz where they enter the Advanced \textsc{ligo} detection band.  This dictated that the longest injection waveform had a duration of {\color{red} 1~777~s}.  In order to guarantee that no two injection waveforms overlapped in the data, the coalescence times of injections were spaced apart by {\color{red} 2~000~$\pm 100$~s}.  For the sake of economizing disk space, we simultaneously analyzed {\color{red} 16 sets} different sets of about $10^3$ injections apiece in the same {\color{red} 14 day} stretch of mock strain data.

Injections were distributed uniformly in log distance.  We used the following heuristic to provide a reasonably balanced number of distant, marginally detectable signals, and nearby, easily detected signals:
$$
d_\mathrm{min} = \frac{1}{2} \cdot \frac{\rho_\mathrm{candle}}{8.0 \cdot \min {d_\mathrm{eff}}}, \quad
d_\mathrm{max} = \frac{1}{4} \cdot \frac{\rho_\mathrm{candle}}{5.5 \cdot \max {d_\mathrm{eff}}}.
$$
Here, $\rho_\mathrm{candle}$ is a fiducially selected \textsc{snr}, and $d_\mathrm{eff}$ is the distance at which a face-on-system would produce a matched filter \textsc{snr} of $\rho_\mathrm{candle}$.

Orientations of injection sources are drawn uniformly, such that the sky location is distributed uniformly in $4\pi$ and the cosine of the binary inclination angle $\iota$ is distributed uniformly in $[0, \pi]$.
